Evaluation of probabilistic photometric redshift estimation approaches for \textsc{LSST}

### 2019-12-17 paper/tex/discussion.tex

\section{Discussion and future work}
\label{sec:discussion}
%(Sam Schmidt, Ofer Lahav, Jeff Newman, Alex Malz, Eve Kovacs, Tony Tyson, Tina Peters)
In contrast with other \pzpdf\ comparison papers that have aimed to identify the ``best'' code for a given survey, we have focused on the somewhat more philosophical questions of how to assess \pzpdf\ methods and how to interpret differences between codes in terms of \pzpdf\ performance.
In Section~\ref{sec:caution}, we reframe the strong performance of our pathological \pzpdf\ technique, \trainz, as a cautionary tale about the importance of choosing appropriate comparison metrics.
In Section~\ref{sec:futureexperiments}, we outline the experiments we intend to build upon this study.
In Section~\ref{sec:futuredata}, we discuss the enhancements of the mock data set that will be necessary to enable the future experiments.

\subsection{Interpretation of metrics}
\label{sec:caution}
%(Alex Malz, Sam Schmidt)

@@

The \trainz\ estimator of Section~\ref{sec:trainz}, which assigns every galaxy a \pzpdf\ equal to $N(z)$ of the training set, is introduced as an experimental control or null test to demonstrate this point via \textit{reductio ad absurdum}.
Because our training set is perfectly representative of the test set, $N(z)$ should be identical for both sets down to statistical noise.
\textbf{We make the alarming observation that \trainz, the absurd experimental control, outperforms all codes on the CDF-based metrics, and all but one code on the $N(z)$ based statistics.}
The PIT and other CDF-based metrics upon which modern \pzpdf\ comparisons are built \citep{Bordoloi:10,Polsterer:16,Tanaka:17} can be gamed by a trivial estimator that yields only an affirmation of prior knowledge uninformed by the data.
In other words, such ensemble metrics are insufficient for the task of selecting \pzpdf\ codes for analysis pipelines\footnote{That being said, we note that close relatives of \trainz\ have been employed by weak lensing surveys of the past and present \citep{Lima:08, Hildebrandt:17, Hoyle:18} to estimate $N(z)$ by assigning each test set galaxy the redshift distribution of a \emph{subset} of the training set, where the subset is defined as similar to the test set galaxy in the space of photometric data.
The specific science goal naturally guides the choice of metric to focus on $N(z)$ rather than individual \pzpdf s, and on the basis of that metric such improvements upon \trainz\ are guaranteed to be more robust to training set imbalance.}.
%\textit{Explain the connection between \trainz\ and these metrics.}

@@

% While looking at one, or even most of our metrics would have given the impression that this estimator was nearly optimal, red flags in CDE loss and point estimates reveal the problems.
%[more caution on over-reliance on metrics, and making sure that metrics test all of what you want] \red{this definitely still needs work}
In summary, context is crucial to defend against deceptively strong performers such as \trainz;
\textbf{the best \pzpdf\ method is the one that most effectively achieves the science goals of a particular study}, not the one that performs best on a metric that does not reflect those goals.
In the absence of a single scientific motivation or the information necessary for a principled metric definition, we must consider many metrics and be critical of the information transmitted by each.
% As stated earlier, science applications may be sensitive to individual \pzpdf s, \pzpdf\ ensembles, \pz\ point estimates, or science-specific statistics like $\hat{N}(z)$.
% We must be aware of that the optimal method for one is not necessarily optimal for the other, and in fact several photo-$z$ algorithms may be necessary in the final cosmological analysis in order to satisfy the requirements of all science use cases.
% The example of the simple \trainz\ estimator described in Section~\ref{sec:caution} shows a simple model with a $p(z)$ that is unrealistic for individual objects can still score very well on many of our metrics.
% It is important to look at {\it all} metrics, and keep in mind what information each metric conveys.
%\aim{[reiterate the meaning of $p(z)$ and the goal -- emphasize finding ``best'' code in terms of impact of assumptions underlying the method \textit{or} establishing methodology for the realistic case of biased prior information and other science goals]}
%\red{[the challenges faced in this project]}
%\red{mention z$<$2, missing some important degeneracies, new sim will go to higher z}
%\red{no quality cuts included, could identify outliers, but could also induce biases}
%\red{[how optimization defined has impact, here we optimized p(z), not n(z), could be science-case specific if stringent requirements are needed, though that may be a computational/storage challenge if too many use cases needed.]}
%\red{some discussion of output parameterization, limitations of 200 point fixed grid, in future switch to something like quantiles (cite qp paper)}

@@

%\begin{enumerate}
%\item \red{the combination of codes}
%\item \red{$p(z,\alpha)$}
%\item \red{tomographic analysis later on}
%\red{this paper deals with training, future papers will also explore calibration via cross-correlation methods}
%\end{enumerate}
%\red{mention the SRM once again, say that the plans are extensive, but we do have a plan and a rough timeline.}

The work presented in this paper is only a first step in assessing \pzpdf\ approaches and moving toward a photometric redshift estimator that will be employed for LSST analyses.  Extensions of the experimental design will require further rounds of analyses, and the authors welcome interest from those outside \lsstdesc\ to have their codes assessed in these future investigations.
%Here we discuss the next steps for subsequent investigations.

@@

%\red{[are there any references for this?  I remember Gary Bernstein talking about this at a photo-z workshop in Japan, but I don't know that it was published.  I believe Michael Troxel has discussed this as well.]}
%\item \red{cosmological parameters in DC2}
%\item \red{mention z$<$2, missing some important degeneracies, new sim will go to higher z}
%\red{no quality cuts included, could identify outliers, but could also induce biases}

@@

Section~\ref{sec:metrics} discussed the difficulty in evaluating PDF accuracy for individual objects with known $(z, d)$ information but without a known $p(z, d)$.
In a follow-up study, we will
 % use generative adversarial networks\citep[(GANs)][]{Goodfellow:14} trained on the simulation data to
generate mock data probabilistically, yielding true PDFs in addition to true redshifts and photometric data.
This future data set will enable tests of PDF accuracy for individual galaxies rather than solely ensembles.

@@

To make optimal use of the \lsst\ data for cosmological and other astrophysical analyses of the \lsstdesc\ SRM, future investigations that build upon this one will require a more sophisticated set of galaxy photometry and redshifts.
%\item \red{inclusion of photometric errors, image based effects, blending, lensing, sky, mask, etc...}
This initial paper explored a data set that was constructed at the catalogue level, with no inclusion of the complications that arise from photometric measurements of imaging data.
Future data challenges will move to catalogues constructed from mock images, including the complications of deblending, sensor inefficiencies, and heterogeneous observing conditions, all anticipated to affect the measured colours of \lsst's galaxy sample \citep{Dawson:2016}.

@@

% In this study we have not accounted for the presence of Active Galactic Nuclei (AGN) contributions to galaxy fluxes.
% In some cases, AGN will be easily identified from the colors and morphologies, i.e. the case of the brightest quasars where the nuclear activity outshines the host galaxy, and numerous studies have utilized color selection to create large samples of quasars \citep[e.g.][]{Richards:06,Maddox:08,Richards:15}.
% In current deep fields, similar in depth to what we expect from \lsst, variability information and multi-wavelength data have been critical to not only identify AGN dominated galaxies, but also obtain more accurate photometric redshifts \citep[e.g][]{Salvato:11}.
%
% In addition to AGN dominated galaxies, those with lower levels of nuclear activity present a more insidious problem, where AGN features may not be apparent, but the colours and other host galaxy properties are perturbed relative to galaxies with an inactive nucleus.
% In such cases, the presence of the AGN may induce a bias if the template SEDs or empirical datasets do not include low-level AGN counterparts.
% For LSST, we will need to identify and obtain accurate photometric redshifts of all types of AGN for a range of science goals, whether it is to eliminate such objects from cosmology experiments, or to use them with confidence, all the way through to understanding galaxy evolution and the role that AGN may play in influencing galaxy properties over cosmic time.

% A promising route to classifying and obtaining accurate photometric redshifts for the AGN population is by combining machine learning with template-fitting techniques, as has recently been demonstrated by \citet{Duncan:18} for radio-selected AGN.
% This is because AGN are relatively easy to obtain spectroscopic redshifts for over all redshifts due to the strong emission lines that they exhibit, allowing very good training sets for machine learning algorithms to use.
% Whereas for those galaxies where the AGN is sub-dominant the galaxy templates are still adequate for obtaining reasonable photometric redshifts.

% In addition to these improvements, the \lsstdesc \Pz\ Working Group plans to look at all potential methods to combine the results from multiple \pzpdf\ codes to improve accuracy, similar to the work presented in \citet{Dahlen:13,Carrascokind:14,Duncan:18}.
% Taking advantage of multiple algorithms that use observables in slightly different ways has shown promise, however we must be very conscious of whether a potential combination properly treats the covariance between the methods, given that they are estimating quantities based on the same underlying observables.
% Several science cases wish to estimate physical quantities along with redshift, for example galaxy stellar mass and star formation rate.
% Proper joint estimation of redshift and physical quantities requires an in depth understanding of galaxy evolution, and progress on accurate bivariate redshift probability distributions will go hand in had with progress on understanding galaxies themselves.
% Parameterization and storage of a complex 2-dimensional probability surface for potentially billions of galaxies (or even subsets of hundreds of thousand of particular interest) pose a potential challenge.
% These issues will be examined in another future paper.

% Finally, while this paper and future papers discussed above focus on photometric redshift codes and estimating accurate \pzpdf s from training data, we plan a separate, but complementary, project to examine calibration of the resultant redshifts via spatial cross-correlations \citep{Newman:2008}, which will be explored in a separate series of future papers.
%The overarching plan describing everything laid out in this section is described in more detail in the \lsstdesc\ Science Roadmap (see Footnote in Section~\ref{sec:intro}).

>>>>

\section{Discussion and future work}
\label{sec:discussion}
In contrast with other \pzpdf\ comparison papers that have aimed to identify the ``best'' code for a given survey, we have focused on the somewhat more philosophical questions of how to assess \pzpdf\ methods and how to interpret differences between codes in terms of \pzpdf\ performance.
In Section~\ref{sec:caution}, we reframe the strong performance of our pathological \pzpdf\ technique, \trainz, as a cautionary tale about the importance of choosing appropriate comparison metrics.
In Section~\ref{sec:futureexperiments}, we outline the experiments we intend to build upon this study.
In Section~\ref{sec:futuredata}, we discuss the enhancements of the mock data set that will be necessary to enable the future experiments.

\subsection{Interpretation of metrics}
\label{sec:caution}

@@

The \trainz\ estimator of Section~\ref{sec:trainz}, which assigns every galaxy a \pzpdf\ equal to $N(z)$ of the training set, is introduced as an experimental control or null test to demonstrate this point via \textit{reductio ad absurdum}.
Because our training set is perfectly representative of the test set, $N(z)$ should be identical for both sets down to statistical noise.
\textbf{We make the alarming observation that \trainz, the absurd experimental control, outperforms all codes on the CDF-based metrics, and all but one code on the $N(z)$ based statistics.}
The PIT and other CDF-based metrics upon which modern \pzpdf\ comparisons are built \citep{Bordoloi:10,Polsterer:16,Tanaka:17} can be gamed by a trivial estimator that yields only an affirmation of prior knowledge uninformed by the data.
In other words, such ensemble metrics are insufficient for the task of selecting \pzpdf\ codes for analysis pipelines\footnote{That being said, we note that close relatives of \trainz\ have been employed by weak lensing surveys of the past and present \citep{Lima:08, Hildebrandt:17, Hoyle:18} to estimate $N(z)$ by assigning each test set galaxy the redshift distribution of a \emph{subset} of the training set, where the subset is defined as similar to the test set galaxy in the space of photometric data.
The specific science goal naturally guides the choice of metric to focus on $N(z)$ rather than individual \pzpdf s, and on the basis of that metric such improvements upon \trainz\ are guaranteed to be more robust to training set imbalance.}.

@@

In summary, context is crucial to defend against deceptively strong performers such as \trainz;
\textbf{the best \pzpdf\ method is the one that most effectively achieves the science goals of a particular study}, not the one that performs best on a metric that does not reflect those goals.
In the absence of a single scientific motivation or the information necessary for a principled metric definition, we must consider many metrics and be critical of the information transmitted by each.

@@

The work presented in this paper is only a first step in assessing \pzpdf\ approaches and moving toward a photometric redshift estimator that will be employed for LSST analyses.  Extensions of the experimental design will require further rounds of analyses, and the authors welcome interest from those outside \lsstdesc\ to have their codes assessed in these future investigations.

@@

@@

Section~\ref{sec:metrics} discussed the difficulty in evaluating PDF accuracy for individual objects with known $(z, d)$ information but without a known $p(z, d)$.
In a follow-up study, we will
generate mock data probabilistically, yielding true PDFs in addition to true redshifts and photometric data.
This future data set will enable tests of PDF accuracy for individual galaxies rather than solely ensembles.

@@

To make optimal use of the \lsst\ data for cosmological and other astrophysical analyses of the \lsstdesc\ SRM, future investigations that build upon this one will require a more sophisticated set of galaxy photometry and redshifts.
This initial paper explored a data set that was constructed at the catalogue level, with no inclusion of the complications that arise from photometric measurements of imaging data.
Future data challenges will move to catalogues constructed from mock images, including the complications of deblending, sensor inefficiencies, and heterogeneous observing conditions, all anticipated to affect the measured colours of \lsst's galaxy sample \citep{Dawson:2016}.

@@
